%-------------------------
% Resume in Latex
% Author : Akshay Rajpurohit
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Akshay Rajpurohit} \\ \vspace{1pt}
    Door No. 202, House No. 3-5-983, Narayanguda, Hyderabad - 500029\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 6309616098 ~ \href{mailto:akj.rajpurohit@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{akj.rajpurohit@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/akshayrajp}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/akshayrajp}}
    \vspace{-8pt}
\end{center}
  
%-----------DEVELOPMENT SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Python, C, C++, HTML/CSS} \\
     \textbf{Technologies}{: Git, Docker} \\
     \textbf{Frameworks/Libraries/Runtimes}{: Spring Boot, React.js, Node.js, Express.js, Bootstrap, Tailwind CSS} \\
     \textbf{Databases}{: MySQL, PostgreSQL, Neo4j, MongoDB, InfluxDB} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Auzmor}{July 2021 -- Present}
      {Full Stack Developer}{Hyderabad, Telangana}
      \resumeItemListStart
        % \resumeItem{Built a Psychometric Test Module for a client with React.js as the front-end and Node.js as the back-end, which sent emails containing the test results using Nodemailer and Google Cloud Platform. Also built a website using WordPress for the same client.}
        % \resumeItem{Built a coupon management system for a client with React.js as front-end and PHP and MySQL as back-end. It was a CRUD project where users could easily add, delete and edit coupons, complete with validation and live feedback to prevent duplicate coupons from being added.}
        % \resumeItem{Built a simple emailing command-line tool to bulk send certificates/documents as attachments to emails stored in JSON format.}
        % \resumeItem{Built a section in a clients website where I added an open source calendar tool highlighting their events using the calendar.}
        % \resumeItem{Built a section in my college club's website where I added a code editor to demonstrate solutions of questions of an event that we conducted.}
        % \resumeItem{Built an info website for a client using Next.js and Tailwind CSS.}
        
     \resumeItemListEnd

    \resumeSubheading
      {Freelancing}{May 2020 -- Present}
      {Full Stack Developer}{Hyderabad, Telangana}
      \resumeItemListStart
        \resumeItem{Built a Psychometric Test Module for a client with React.js as the front-end and Node.js as the back-end, which sent emails containing the test results using Nodemailer and Google Cloud Platform. Also built a website using WordPress for the same client.}
        \resumeItem{Built a coupon management system for a client with React.js as front-end and PHP and MySQL as back-end. It was a CRUD project where users could easily add, delete and edit coupons, complete with validation and live feedback to prevent duplicate coupons from being added.}
        \resumeItem{Built a simple emailing command-line tool to bulk send certificates/documents as attachments to emails stored in JSON format.}
        \resumeItem{Built a section in a clients website where I added an open source calendar tool highlighting their events using the calendar.}
        \resumeItem{Built a section in my college club's website where I added a code editor to demonstrate solutions of questions of an event that we conducted.}
        \resumeItem{Built an info website for a client using Next.js and Tailwind CSS.}
        
     \resumeItemListEnd
     
    \resumeSubheading
        {coding.Studio( );}{January 2020 - March 2021}
        {CP Executive}{Hyderabad, Telangana}
        \resumeItemListStart
          \resumeItem{Founded the CodeChef Campus Chapter in my college and and have been the President for the same since its inception in March 2020. As the President, I have had the opportunity to spearhead the various activities that we have conducted to promote the growth of CP culture in our college. As a result, there has been a considerable growth in the number of participants in monthly CP contests.}
          \resumeItem{Have held the position of Lead in Google Developer Student Club VBIT since August 2020. As the lead, I have promoted the use of Google Cloud Platform Products by enrolling people into the '30 Days of Google Cloud' programme.}
          \resumeItem{Participated In IEEEXtreme 2020 and scored an All India Rank of 16 and Global Rank of 280.}
          
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Remote Monitoring of Environmental Conditions with Telegram Responder Bot} $|$ \emph{Python, C}}{April 2021}
          \resumeItemListStart
            \resumeItem{Developed a Raspberry Pi project that reads the values of sensors (Radiation, Temperature and Humidity) and relays the readings to InfluxDB deployed on an Azure VPS instance on the cloud.}
            \resumeItem{Used Skyhook Precision Location module to determine the geographical location without using a physical GPS module.}
            \resumeItem{Developed a Telegram Bot in Python that fetches data from the InfluxDB and sends a message to the user (Automatic alert messages and on-demand live sensor readings). Also added basic interactivity to the Bot.}
            \resumeItem{Deployed the Bot on the Azure VPS instance so that it is always live.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{studyMap} $|$ \emph{HTML, CSS, JavaScript}}{March 2019}
          \resumeItemListStart
            \resumeItem{Created a web-app that helps students prepare for their exams by generating a tailored exam-prep Time-table for them.}
            \resumeItem{Processed user inputted information (number of days left for the exam, subjects and their respective difficulty ratings) and generated a time-table using those input parameters and printed it out in a PDF format.}
          \resumeItemListEnd 
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{1pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jawaharlal Nehru Technological University, Hyderabad}{Aug. 2017 -- June 2021}
      {Bachelor of Technology in Electronics and Communication Engineerig}{7.4 CGPA}
  \resumeSubHeadingListEnd
  
% \section{Hobbies}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Reading Novels
%                 \item Playing Games
%                 \item Practising CP
%                 \item Watching Movies/TV Shows
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

\end{document}
